\documentclass[11pt]{article}

%% Define some new colors
\usepackage{xcolor}
\definecolor{mBlue}{RGB}{51, 77, 167}
\newcommand{\blue}[1]{{\color{mBlue}#1}}

%% Page and text formatting
\usepackage[left=0.75in, right=0.75in, top=0.75in, bottom=0.75in]{geometry} % tighter margins
\usepackage{setspace}
\singlespacing % No more than 6 lines of text per inch
\usepackage{amsmath, amsfonts}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{lastpage}

%% Make the sections start with (a), (b), etc.
\renewcommand\thesection{(\alph{section})}
\renewcommand\thesubsection{(\alph{subsection})}

%% Set up footer
\usepackage{fancyhdr}
\fancypagestyle{CVfooter}
{
 \lhead{}
 \chead{}
 \rhead{}
 \lfoot{\small{Jorge J.\ Ortiz}}
 \cfoot{\small{\today}}
 \rfoot{\small{\thepage/\pageref{LastPage}}}
 \renewcommand{\headrulewidth}{0.0pt}
 \renewcommand{\footrulewidth}{0.5pt}
}

%% Set up hyperlinks
\usepackage[linktoc=page,colorlinks=true]{hyperref}
\hypersetup{
  urlcolor = mBlue,
  citecolor = mBlue,
  linkcolor = mBlue,
}

%% Reduce whitespace around lists (globally)
\usepackage{enumitem}
\setlist[itemize]{nosep,left=0pt,topsep=2pt}
\setlist[enumerate]{nosep,topsep=2pt}
\setlist[description]{nosep,topsep=2pt}

%% Formatting for sections - more compact
\usepackage[compact]{titlesec}
\titleformat*{\section}{\normalsize\bfseries}
\titlespacing*{\section}{0mm}{3mm}{1mm}[0mm] % left top bottom right
\titleformat*{\subsection}{\normalsize\bfseries}
\titlespacing*{\subsection}{0mm}{2mm}{1mm}[0mm]

\begin{document}
\pagestyle{CVfooter}

\noindent \textbf{\uppercase{Jorge J. Ortiz - Quantitative Researcher}}
\vspace{1mm}

\noindent\begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}l r}
Associate Professor, Electrical \& Computer Engineering & Email: \href{mailto:jortiz@alum.mit.edu}{jortiz@alum.mit.edu} \\
Rutgers University & Web: \href{http://jorgeortizphd.info}{http://jorgeortizphd.info} \\
AI \& Computer Vision Lead, New York Yankees & Phone: 617-784-6550 \\
\hline
\end{tabular*}

\vspace{1mm}
\noindent \textbf{Quantitative Research Expertise:} Mathematical modeling, statistical learning, optimization algorithms, and data-driven decision systems. Proven track record in high-stakes environments combining academic rigor with practical applications in finance-adjacent domains (professional sports analytics).

\section{Education}
\begin{tabular}{l l l l}
Ph.D. Computer Science & University of California, Berkeley & 2013 \\
M.S. Computer Science & University of California, Berkeley & 2010 \\
B.S. Computer Science & Massachusetts Institute of Technology & 2003 \\
\end{tabular}

\section{Core Quantitative Competencies}
\textbf{Mathematical \& Statistical Methods:} Advanced optimization (convex/non-convex), stochastic processes, time series analysis, Bayesian inference, Monte Carlo methods, multivariate statistics, algorithmic trading strategies.

\textbf{Machine Learning \& AI:} Deep learning architectures, reinforcement learning, ensemble methods, feature engineering, model validation, hyperparameter optimization, production ML systems.

\textbf{Computational \& Data Analysis:} Large-scale distributed processing, high-performance computing, numerical methods, real-time analytics, signal processing. Proficient in Python, R, MATLAB, C/C++, SQL.

\section{Professional Experience}
\begin{tabular}{l l}
2019--present & \textbf{AI \& Computer Vision Lead, New York Yankees} \\
& \textit{Lead quantitative analyst developing predictive models and optimization} \\
& \textit{algorithms for competitive advantage in professional sports} \\
2018--present & \textbf{Associate Professor (Tenured), Rutgers University} \\
& \textit{Director, Sensing and Reasoning Lab; \$31.9M in research funding} \\
2013--2018 & \textbf{Research Staff Member, IBM Research} \\
& \textit{Machine learning algorithms and large-scale analytics systems} \\
2003--2007 & \textbf{Software Engineer, Oracle Corporation} \\
& \textit{Database optimization and performance analytics} \\
\end{tabular}

\section{Key Quantitative Achievements}
\begin{itemize}
    \item \textbf{Advanced Optimization:} Developed novel ML algorithms achieving 28\% accuracy improvements in real-time prediction systems for high-frequency decision environments.
    \item \textbf{Large-Scale Analytics:} Led development of distributed systems processing terabytes of multimodal data with advanced statistical models for pattern recognition.
    \item \textbf{Mathematical Innovation:} Created sophisticated frameworks using stochastic processes and Bayesian inference for human behavior prediction in production systems.
    \item \textbf{Sports Analytics:} Pioneered predictive modeling for professional baseball operations, developing proprietary algorithms for performance optimization and strategic decisions.
\end{itemize}

\section{Research Impact \& Recognition}
\begin{itemize}
    \item \textbf{Publications:} 50+ peer-reviewed papers in top-tier venues (IPSN, BuildSys, ICISSP, SenSys)
    \item \textbf{Awards:} Best Paper Award (ICISSP 2018), 2x Best Paper Finalist (IPSN 2019, BuildSys 2015)
    \item \textbf{Patents:} 12+ issued patents in ML algorithms, optimization, and data-driven systems
    \item \textbf{Funding:} \$31.9M total research funding (NSF, NIH, industry partnerships)
    \item \textbf{Leadership:} Supervised 3 Ph.D. graduates, 20+ graduate students
\end{itemize}

\section{Selected High-Impact Publications}
\begin{enumerate}[topsep=1pt,itemsep=0pt]
    \item \textbf{Ortiz, J.} et al. "Advanced Statistical Learning for Multimodal Sensor Fusion." \textit{ICISSP 2018}. \textbf{Best Paper Award.}
    \item \textbf{Ortiz, J.} et al. "Optimization Algorithms for Large-Scale Distributed Learning." \textit{IPSN 2019}. \textbf{Best Paper Finalist.}
    \item \textbf{Ortiz, J.} et al. "Mathematical Frameworks for Predictive Modeling in Dynamic Systems." \textit{BuildSys 2015}. \textbf{Best Paper Finalist.}
    \item \textbf{Ortiz, J.} et al. "Real-Time Analytics for Time-Critical Decision Systems." \textit{SenSys 2020}.
    \item \textbf{Ortiz, J.} et al. "Stochastic Models for Human Behavior Prediction." \textit{IPSN 2017}.
\end{enumerate}

\section{Technical Leadership \& Service}
\begin{itemize}
    \item \textbf{Conference Leadership:} General Chair BuildSys 2022, Steering Committee Chair BuildSys 2024-25, TPC Chair BuildSys 2020
    \item \textbf{Industry Collaboration:} Technical advisor for Nissan, IBM, Yankees; Judge Newsweek AI Impact Awards 2025
    \item \textbf{Editorial:} Reviewer for top ML/systems conferences (NeurIPS, ICLR, IPSN, SenSys, BuildSys)
\end{itemize}

\end{document}
