\documentclass[11pt]{article}

%% Define colors and formatting
\usepackage{xcolor}
\definecolor{mBlue}{RGB}{51, 77, 167}
\definecolor{lightGray}{RGB}{240, 240, 240}
\definecolor{darkGray}{RGB}{85, 85, 85}
\newcommand{\blue}[1]{{\color{mBlue}#1}}

%% Page formatting
\usepackage[left=0.75in, right=0.75in, top=0.6in, bottom=0.6in]{geometry}
\usepackage{setspace}
\usepackage{amsmath, amsfonts}
\usepackage[T1]{fontenc}
\usepackage{times}
\usepackage{lastpage}

%% Graphics for design elements
\usepackage{tikz}
\usepackage{graphicx}

%% Hyperlinks
\usepackage[colorlinks=true]{hyperref}
\hypersetup{
  urlcolor = mBlue,
  citecolor = mBlue,
  linkcolor = mBlue,
}

%% Lists
\usepackage{enumitem}
\setlist[itemize]{nosep,left=0pt,leftmargin=12pt}

%% Section formatting with lines
\usepackage[compact]{titlesec}
\titleformat{\section}
  {\large\bfseries\color{mBlue}}
  {}
  {0em}
  {\titlerule[1pt]\vspace{1pt}\titlerule[0.5pt]\vspace{2pt}}
\titlespacing*{\section}{0mm}{6mm}{3mm}[0mm]

\titleformat*{\subsection}{\normalsize\bfseries\color{darkGray}}
\titlespacing*{\subsection}{0mm}{3mm}{1mm}[0mm]

%% No page numbers
\pagestyle{empty}

%% Custom commands for prettier formatting
\newcommand{\bulletpoint}{\textcolor{mBlue}{$\bullet$}}
\newcommand{\divider}{\vspace{1mm}\noindent\makebox[\linewidth]{\textcolor{lightGray}{\rule{0.8\linewidth}{0.5pt}}}\vspace{1mm}}
\newcommand{\positionentry}[4]{
  \textbf{#1} \hfill \textcolor{darkGray}{\textit{#2}}\\
  \textcolor{darkGray}{#3} \hfill #4
}

\begin{document}

% Header with elegant design
\begin{center}
\begin{tikzpicture}
\node[inner sep=0pt] at (0,0) {
\begin{minipage}{\textwidth}
\centering
{\Huge \textbf{\textcolor{mBlue}{Jorge J. Ortiz}}}\\[3mm]
{\large Associate Professor (with Tenure) \bulletpoint\ Electrical and Computer Engineering}\\[1mm]
{\large Director, Sensing and Reasoning (SnR) Lab}\\[2mm]
{\textbf{\textcolor{darkGray}{Rutgers University}}}\\[3mm]
\textcolor{mBlue}{\rule{0.6\textwidth}{1pt}}\\[2mm]
\href{mailto:jorge.ortiz@rutgers.edu}{\textcolor{mBlue}{jorge.ortiz@rutgers.edu}} \bulletpoint\ 
\href{http://jorgeortizphd.info}{\textcolor{mBlue}{jorgeortizphd.info}} \bulletpoint\ 
\textcolor{darkGray}{617-784-6550}
\end{minipage}
};
\end{tikzpicture}
\end{center}

\vspace{4mm}

\section{Education}
\positionentry{Ph.D., Computer Science}{2013}{University of California, Berkeley}{}\\[1mm]
\positionentry{M.S., Computer Science}{2010}{University of California, Berkeley}{}\\[1mm]
\positionentry{B.S., Computer Science}{2003}{Massachusetts Institute of Technology}{}

\section{Academic Appointments}
\positionentry{Associate Professor (with Tenure)}{Sept. 2025 -- present}{Rutgers University}{}\\[1mm]
\positionentry{Assistant Professor}{Sept. 2018 -- 2025}{Rutgers University}{}

\section{Research Leadership}
\positionentry{Director, Sensing and Reasoning (SnR) Lab}{Sept. 2018 -- present}{Rutgers University}{}

\section{Industry Experience}
\positionentry{AI and Computer Vision Lead, Baseball Operations}{Dec. 2019 -- present}{New York Yankees}{}\\[1mm]
\positionentry{Research Staff Member}{Dec. 2013 -- Aug. 2018}{IBM Research}{}

\section{Research Areas}
\begin{center}
\textcolor{darkGray}{
\textbf{Multimodal Learning and AI} \bulletpoint\ \textbf{Human-Computer Interaction} \bulletpoint\ \textbf{IoT and Smart Environments}\\[1mm]
\textbf{Computer Vision and Sensing} \bulletpoint\ \textbf{Machine Learning Applications}
}
\end{center}

\section{Key Honors \& Recognition}
\begin{itemize}
\item \textbf{\textcolor{mBlue}{Judge}}, Newsweek AI Impact Awards 2025
\item \textbf{\textcolor{mBlue}{Keynote Speaker}}, Workshop on Smart and Connected Indoor Environments (IEEE SECON 2017)
\item \textbf{\textcolor{mBlue}{Best Paper Awards}}: ICISSP 2018, \textbf{Best Paper Finalists}: IoTDI 2019, BuildSys 2015 (2x)
\item \textbf{\textcolor{mBlue}{Invited Panelist}}: JPMC Hispanic Heritage Month Tech Panel, Sports and AI Symposium (Columbia)
\item NSF Graduate Fellowship Honorable Mention, Qualcomm Innovation Fellowship Finalist
\end{itemize}

\section{Major Grants \& Funding (\$6.9M+)}
\begin{itemize}
\item \textbf{\textcolor{mBlue}{NSF ReDDDoT Phase 2}}: Urban AI in Harlem, Co-PI \textbf{(\$1.45M)}
\item \textbf{\textcolor{mBlue}{NIH CAMERA Platform}}: Development, Co-PI \textbf{(\$1.08M)}
\item \textbf{\textcolor{mBlue}{NSF Engineering Research Center}}: Smart Streetscapes, Site PI \textbf{(\$2.3M)} Rutgers portion of \$26M
\item \textbf{\textcolor{mBlue}{NSF IUCRC}}: Standards and Ethics in AI, PI \textbf{(\$20K)}
\end{itemize}

\section{Selected Publications}
\begin{itemize}
\item \textbf{J. Ortiz} et al., ``DeviceMien: Network Device Behavior Modeling for Identifying Unknown IoT Devices,'' \textit{ACM IoTDI}, 2019. \textbf{\textcolor{mBlue}{[Best Paper Finalist]}}
\item M. Aldeer, \textbf{J. Ortiz}, et al., ``PatientSense: Patient Discrimination from in-Bottle Sensors Data,'' \textit{ACM MobiQuitous}, 2019.
\item Y. Sun, N. Salami Pargoo, P. Jin, \textbf{J. Ortiz}, ``Optimizing Autonomous Driving for Safety: A Human-Centric Approach with LLM-Enhanced RLHF,'' \textit{ACM UbiComp Companion}, 2024.
\item Z. Hussain et al., ``Non-Invasive Techniques for Monitoring Different Aspects of Sleep: A Comprehensive Review,'' \textit{ACM Trans. Computing for Healthcare}, 2022.
\item D. Hong, H. Wang, \textbf{J. Ortiz}, K. Whitehouse, ``The Building Adapter: Towards Quickly Applying Building Analytics at Scale,'' \textit{ACM BuildSys}, 2015. \textbf{\textcolor{mBlue}{[Best Paper Finalist]}}
\item A. Bhattacharya et al., ``Automated Metadata Construction to Support Portable Building Applications,'' \textit{ACM BuildSys}, 2015. \textbf{\textcolor{mBlue}{[Best Paper Finalist]}}
\end{itemize}

\section{Students \& Mentoring}
\textbf{\textcolor{mBlue}{Ph.D. Graduates:}} Tahiya Chowdhury (2022), Murtadha Aldeer (2023), Tong Wu (2023)\\[1mm]
\textbf{\textcolor{mBlue}{Research Focus:}} Human activity sensing, multimodal learning, IoT behavior understanding

\section{Selected Professional Service}
\begin{itemize}
\item \textbf{\textcolor{mBlue}{Leadership:}} Steering Committee Chair BuildSys (2024-25), General Chair BuildSys (2022)
\item \textbf{\textcolor{mBlue}{2025 TPC:}} ACM MobiHoc, Sensys, Buildsys, ICLR
\item \textbf{\textcolor{mBlue}{Major Workshops:}} NeurIPS 2021 Deep Learning \& Differential Equations (Organizer)
\item \textbf{\textcolor{mBlue}{Conference Organization:}} CPS-IoT Week 2019 Publication Chair (5 conferences)
\end{itemize}

\section{Patents}
\begin{center}
\textbf{\textcolor{darkGray}{12+ issued patents}} in IoT, sensing, and machine learning applications
\end{center}

\end{document} 